The \dealii{} Library, Version 9.3

### 2021-06-18 9.3/paper.tex
Add a sentence.
Add Bruno's name & address.

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Marc Fehling,
    Rene Gassm{\"o}ller
    Timo Heister,
    Luca Heltai,
    Uwe K{\"o}cher,
    Martin Kronbichler,
    Matthias Maier,
    Peter Munch,
    Jean-Paul Pelteret,
    Sebastian Proell,
    Konrad Simon,
    Bruno Turcksin,
    David Wells,
    Jiaqi Zhang
  },
  pdftitle={The deal.II Library, Version 9.3, 2021},
}

@@

@@

\author[4]{Rene~Gassm{\"o}ller}
\affil[4]{Department of Geological Sciences,
   University of Florida,
   1843 Stadium Road,
   Gainesville, FL, 32611, USA.
  {\texttt{rene.gassmoeller@ufl.edu}}}

\author[5]{Timo~Heister}
 \affil[5]{School of Mathematical and Statistical Sciences,
   Clemson University,
   Clemson, SC, 29634, USA
   {\texttt{heister/jiaqi2@clemson.edu}}}

\author[6]{Luca~Heltai}
\affil[6]{SISSA,
   International School for Advanced Studies,
   Via Bonomea 265,
   34136, Trieste, Italy.
   {\texttt{luca.heltai@sissa.it}}}

\author[7]{Uwe~K{\"o}cher}
\affil[7]{Chair of Numerical Mathematics,
  Helmut-Schmidt-University,
  University of the Federal Armed Forces Hamburg,
  Holstenhofweg~85, 22043 Hamburg, Germany.
  {\texttt{uwe.koecher@hsu-hh.de}}}

 \author[8,9]{Martin~Kronbichler}
 \affil[8]{Institute for Computational Mechanics,
   Technical University of Munich,
   Boltzmannstr.~15, 85748 Garching, Germany.
   {\texttt{kronbichler/munch/proell@lnm.mw.tum.de}}}
 \affil[9]{Department of Information Technology,
   Uppsala University,
   Box 337, 751\,05 Uppsala, Sweden.
   {\texttt{martin.kronbichler@it.uu.se}}}

\author[10]{Matthias~Maier}
\affil[10]{Department of Mathematics,
  Texas A\&M University,
  3368 TAMU,
  College Station, TX 77845, USA.
  {\texttt{maier@math.tamu.edu}}}

\author[8,11]{Peter Munch}
 \affil[11]{Institute of Materials Research, Materials Mechanics,
 Helmholtz-Zentrum Geesthacht,
 Max-Planck-Str. 1, 21502 Geesthacht, Germany.
   {\texttt{peter.muench@hzg.de}}}

\author[12]{Jean-Paul~Pelteret}
\affil[12]{Independent researcher.
{\texttt{jppelteret@gmail.com}}}

\author[8]{Sebastian~Proell}

\author[13]{Konrad Simon}
  \affil[13]{Department of Mathematics/Center for Earth System Research and Sustainability (CEN),
  University of Hamburg, Grindelberg 5, 20144 Hamburg, Germany}

@@

\author[14]{David Wells}
\affil[14]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

\author[5]{Jiaqi~Zhang}

@@

\item \texttt{step-79} is a program for topology optimization. Written
  by Justin O'Connor at Colorado State University, the program asks
  what the optimal distribution of a finite amount of material in a
  domain is to maximize its strength (or optimize some other objective
  functional). It uses advanced optimization techniques.
\end{itemize}

>>>>

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Bruno Blais,
    Marc Fehling,
    Rene Gassm{\"o}ller
    Timo Heister,
    Luca Heltai,
    Uwe K{\"o}cher,
    Martin Kronbichler,
    Matthias Maier,
    Peter Munch,
    Jean-Paul Pelteret,
    Sebastian Proell,
    Konrad Simon,
    Bruno Turcksin,
    David Wells,
    Jiaqi Zhang
  },
  pdftitle={The deal.II Library, Version 9.3, 2021},
}

@@

\author[4]{Bruno Blais}
\affil[4]{Research Unit for Industrial Flows Processes (URPEI), Department of Chemical Engineering,
          Polytechnique Montréal,
          PO Box 6079, Stn Centre-Ville, Montréal, Québec, Canada, H3C 3A7.
          {\texttt{bruno.blais@polymtl.ca}}}

@@

\author[5]{Rene~Gassm{\"o}ller}
\affil[5]{Department of Geological Sciences,
   University of Florida,
   1843 Stadium Road,
   Gainesville, FL, 32611, USA.
  {\texttt{rene.gassmoeller@ufl.edu}}}

\author[6]{Timo~Heister}
 \affil[6]{School of Mathematical and Statistical Sciences,
   Clemson University,
   Clemson, SC, 29634, USA
   {\texttt{heister/jiaqi2@clemson.edu}}}

\author[7]{Luca~Heltai}
\affil[7]{SISSA,
   International School for Advanced Studies,
   Via Bonomea 265,
   34136, Trieste, Italy.
   {\texttt{luca.heltai@sissa.it}}}

\author[8]{Uwe~K{\"o}cher}
\affil[8]{Chair of Numerical Mathematics,
  Helmut-Schmidt-University,
  University of the Federal Armed Forces Hamburg,
  Holstenhofweg~85, 22043 Hamburg, Germany.
  {\texttt{uwe.koecher@hsu-hh.de}}}

 \author[9,10]{Martin~Kronbichler}
 \affil[9]{Institute for Computational Mechanics,
   Technical University of Munich,
   Boltzmannstr.~15, 85748 Garching, Germany.
   {\texttt{kronbichler/munch/proell@lnm.mw.tum.de}}}
 \affil[10]{Department of Information Technology,
   Uppsala University,
   Box 337, 751\,05 Uppsala, Sweden.
   {\texttt{martin.kronbichler@it.uu.se}}}

\author[11]{Matthias~Maier}
\affil[11]{Department of Mathematics,
  Texas A\&M University,
  3368 TAMU,
  College Station, TX 77845, USA.
  {\texttt{maier@math.tamu.edu}}}

\author[9,12]{Peter Munch}
 \affil[12]{Institute of Materials Research, Materials Mechanics,
 Helmholtz-Zentrum Geesthacht,
 Max-Planck-Str. 1, 21502 Geesthacht, Germany.
   {\texttt{peter.muench@hzg.de}}}

\author[13]{Jean-Paul~Pelteret}
\affil[13]{Independent researcher.
{\texttt{jppelteret@gmail.com}}}

\author[9]{Sebastian~Proell}

\author[14]{Konrad Simon}
  \affil[14]{Department of Mathematics/Center for Earth System Research and Sustainability (CEN),
  University of Hamburg, Grindelberg 5, 20144 Hamburg, Germany}

@@

\author[15]{David Wells}
\affil[15]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

\author[6]{Jiaqi~Zhang}

@@

\item \texttt{step-79} is a program for topology optimization. Written
  by Justin O'Connor at Colorado State University, the program asks
  what the optimal distribution of a finite amount of material in a
  domain is to maximize its strength (or optimize some other objective
  functional). It uses advanced optimization techniques to deal with
  the nonlinearity of the problem as well as with the equality and
  inequality constraints that characterize the application.
\end{itemize}
